---
title: "Assessment 1.1: Data Types"
output:
    github_document:
        toc: TRUE
---
#### *Assessment 1.1 has 5 parts. Each of the 5 parts includes instructions and hints.*

### Instructions: Part 1, Variable Names
The type of data we are working with will often influence the data visualization technique we use. We will be working with two types of variables: categorical and numeric. Each can be divided into two other groups: categorical can be ordinal or not, whereas numerical variables can be discrete or continuous.

We will review data types using some of the examples provided in the `dslabs` package. For example, the `heights` dataset.
```
library(dslabs)
data(heights)
```
##### Instructions
Let's start by reviewing how to extract the variable names from a dataset using the `names` function. Write the code to reveal the two variable `names` used in the `heights` dataset.
```{r}
library(dslabs)
data(heights)
names(heights)
```
### Instructions: Part 2, Variable Types
We saw that `sex` is the first variable. Confirm that the values that are represented by this variable are categorical by looking at the first few entries using `library()`, `data()`, and `head()`.
```{r}
head(heights)
```

### Instructions: Part 3, Numerical Values
Keep in mind that discrete numeric data can be considered ordinal. Although this is technically true, we usually reserve the term ordinal data for variables belonging to a small number of different groups, with each group having many members.

The `height` variable could be ordinal if, for example, we report a small number of values such as short, medium, and tall. Let's explore how many unique values are used by the heights variable. For this we can use the `unique` function:
```
x <- c(3, 3, 3, 3, 4, 4, 2)
unique(x)
```
##### Instructions
Use the `unique` and `length` functions to determine how many unique heights were reported.
```{r}
x <- heights$height
length(unique(x))
```

### Instructions: Part 4, Tables
One of the useful outputs of data visualization is that we can learn about the distribution of variables. For categorical data, we can construct this distribution by simply computing the frequency of each unique value. This can be done with the function `table`. Here is an example:
```
x <- c(3, 3, 3, 3, 4, 4, 2)
table(x)
```
##### Instructions
Use the `table` function to compute the frequencies of each unique height value. Because we are using the resulting frequency table in a later exercise we want you to save the results into an object and call it `tab`.
```{r}
tab <- table(x)
```
### Instructions: Part 5, Indicator Variables
To see why treating the reported heights as an ordinal value is not useful in practice, we note how many values are reported only once.

##### Instructions
In the previous exercise we computed the variable `tab` which reports the number of times each unique value appears. For values reported only once `tab` will be 1. Use logicals and the function `sum` to count the number of times this happens.
```{r}
sum(tab == 1)
```